Practical Challenges with Web Service Evolution:\\A Review of Literature and Current Industry Practices

### 2013-06-05 paper.tex
corrected a paragraph connection

After the screening process, we had a shortlist of articles to extract information from. In the next paragraphs, we discuss the findings from these sources in light of the research questions.

>>>>

In the next section, we list and discuss our findings from these selected papers in light of the research questions.
